Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-23 2016_ICML/appendix.tex
Adding apendix to main paper

\section{Synthetic Single-Task Benchmark with Model Mismatch}

@@

We present results for an identical setup as reported in Section 5.1, with the
only difference being that the test functions have been sampled from a GP with
rational quadratic kernel with length scale $l=0.1$ and scale mixture
$\alpha=1.0$. The kernel used in the GP surrogate model is not modified, i.e.,
an RBF kernel with length scale $l=0.1$ is used. Thus, since different kind of
kernel govern test functions and surrogate model, we have model mismatch as
would be the common case on real-world problems. Figure
\ref{fig:empirical_comparison_mm} summarizes the results of the experiment.
Interestingly, in contrast to the experiment without model mismatch, for this setup
there are also considerable differences in the mean simple regret between MRS
and ES: while ES performs slightly better initially, it is outperformed by MRS
for $N > 60$. We suspect that this is because ES tends to explore more locally
than MRS once $p^\star$ has mostly settled onto one region of the search
space. More local exploration, however, can be detrimental in the case of
model-mismatch since the surrogate model is more likely to underestimate the
function value in regions which have not been sampled. Thus a more homogeneous
sampling of the search space as done by the more global exploration of MRS is
beneficial. As a second observation, in contrast to a no-model-mismatch
scenario, MRS$^\text{point}$ performs considerably worse than MRS when there
is model-mismatch. This emphasizes the importance of accounting for
uncertainty, particularly when there is model mis-specification.

>>>>

\section{Synthetic Single-Task Benchmark with Model Mismatch}
\label{section:exp_model_mismatch}

@@

We present results for an identical setup as reported in Section \ref{Section:ResultsSingleTask},
with the
only difference being that the test functions have been sampled from a GP with
rational quadratic kernel with length scale $l=0.1$ and scale mixture
$\alpha=1.0$. The kernel used in the GP surrogate model is not modified, i.e.,
an RBF kernel with length scale $l=0.1$ is used. Thus, since different kind of
kernel govern test functions and surrogate model, we have model mismatch as
would be the common case on real-world problems. Figure
\ref{fig:empirical_comparison_mm} summarizes the results of the experiment.
Interestingly, in contrast to the experiment without model mismatch, for this setup
there are also considerable differences in the mean simple regret between MRS
and ES: while ES performs slightly better initially, it is outperformed by MRS
for $N > 60$. We suspect that this is because ES tends to explore more locally
than MRS once $p^\star$ has mostly settled onto one region of the search
space. More local exploration, however, can be detrimental in the case of
model-mismatch since the surrogate model is more likely to underestimate the
function value in regions which have not been sampled. Thus a more homogeneous
sampling of the search space as done by the more global exploration of MRS is
beneficial. As a second observation, in contrast to a no-model-mismatch
scenario, MRS$^\text{point}$ performs considerably worse than MRS when there
is model-mismatch. This emphasizes the importance of accounting for
uncertainty, particularly when there is model mis-specification.

### 2016-05-23 2016_ICML/cmrs.tex
Adding apendix to main paper

In the first experiment\footnote{Source code for replicating the reported experiment
is available under \url{https://github.com/jmetzen/bayesian_optimization}.}, 
we conduct a similar analysis as \citet[Section
3.1]{hennig_entropy_2012}: we compare different algorithms on a number of
single-task functions sampled from a generative model, namely from the same GP-based model
that is used by the optimization internally as surrogate model. This precludes
model-mismatch issues and unwanted bias which could be introduced by resorting
to common hand-crafted test functions\footnote{Please refer to the supplementary material for an analogous experiment with model-mismatch.}. More specifically, we choose the
parameter space to be the 2-dimensional unit domain $\mathcal{X} = [0, 1]^2$ and generate test
functions by sampling $250$ function values jointly from a GP with an isotropic RBF kernel
of length scale $l = 0.1$ and unit signal variance. A GP is
fitted to these function values and the resulting posterior mean is used as the
test function. Moreover, Gaussian noise with standard deviation $\sigma =
10^{-3}$ is added to each observation. The GP used as surrogate model in the optimizer employed the same 
isotropic RBF kernel with fixed, identical hyperparameters. 
In order to isolate effects of the different acquisition functions from effects of different
recommendation mechanisms, we used the point which maximizes the GP posterior
mean as recommendation $\mathbf{\tilde x}_N$ regardless of the employed acquisition function.
All algorithms were tested on the same
set of $250$ test functions, and we used $n_f=1000$, $n_r=25$, and $n_y=51$.
We do not provide error-bars on the estimates as the data sets have no parametric distribution. 
However, we provide additional histograms on the regret distribution.

@@

%\newpage
%\appendix 
%\input{appendix.tex}

>>>>

In the first experiment\footnote{Source code for replicating the reported experiment
is available under \url{https://github.com/jmetzen/bayesian_optimization}.}, 
we conduct a similar analysis as \citet[Section
3.1]{hennig_entropy_2012}: we compare different algorithms on a number of
single-task functions sampled from a generative model, namely from the same GP-based model
that is used by the optimization internally as surrogate model. This precludes
model-mismatch issues and unwanted bias which could be introduced by resorting
to common hand-crafted test functions\footnote{Please refer to the Appendix \ref{section:exp_model_mismatch} for an analogous experiment with model-mismatch.}. More specifically, we choose the
parameter space to be the 2-dimensional unit domain $\mathcal{X} = [0, 1]^2$ and generate test
functions by sampling $250$ function values jointly from a GP with an isotropic RBF kernel
of length scale $l = 0.1$ and unit signal variance. A GP is
fitted to these function values and the resulting posterior mean is used as the
test function. Moreover, Gaussian noise with standard deviation $\sigma =
10^{-3}$ is added to each observation. The GP used as surrogate model in the optimizer employed the same 
isotropic RBF kernel with fixed, identical hyperparameters. 
In order to isolate effects of the different acquisition functions from effects of different
recommendation mechanisms, we used the point which maximizes the GP posterior
mean as recommendation $\mathbf{\tilde x}_N$ regardless of the employed acquisition function.
All algorithms were tested on the same
set of $250$ test functions, and we used $n_f=1000$, $n_r=25$, and $n_y=51$.
We do not provide error-bars on the estimates as the data sets have no parametric distribution. 
However, we provide additional histograms on the regret distribution.

@@

\newpage
\appendix 
\input{appendix.tex}
